---
title: "Problems and Solutions to Compile a PDF Version of Advanced R"
author:"Sunrongxue"
output: html_document
---

R version is 3.6.3

## When I open the project(Adv-r.Rproj) using Rstudio:  
Error in loadNamespace(name) : there is no package called ‘bookdown’

so I install the package bookdown by
```{r eval=FALSE}
install.packages("bookdown")
```
but it didn't work with error:package ‘bookdown’ is not available (for R version 3.6.3) 
then I change the CRANmirror by
```{r eval=FALSE}
chooseCRANmirror()
```

## And then I compile the book:
```{r eval=FALSE}
bookdown::render_book("index.Rmd",output_format="bookdown::pdf_book")
```

## Problems and solutions during the building process

Problem 1

Quitting from lines 223-235 (Introduction.Rmd) 
Error in cat(paste0(contributors$desc, collapse = ", ")) : 

Solution:adding encoding="UTF-8" in line 224 of introduction.rmd to fix it.
```{r eval=FALSE}
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE, encoding = "UTF-8")
```

Problem 2

Error in loadNamespace(name) : there is no package called "..."

Solution:install some packages by
```{r eval=FALSE}
install.packages()"knitr","desc","sessioninfo","lobstr","ggplot2","devtools","sloop","DBI","RSQLite","profvis","bench","tidyr",
```

Problem 3 

Error in loadNamespace(name) : there is no package called "emo"
Calls: local ... loadNamespace -> withRestarts -> withOneRestart -> doWithOneRestart

I can't use "install.packages" to download this packages

Solution:use devtools to install the package from github
```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("hadley/emo")
```
but there is a new problem

Error in .f(.x[[i]], .y[[i]], ...) : Can't open URL'https://adv-r.hadley.nz'
I'm still looking for a solution


to be continued
